CdGF_aucrf

### 2017-01-11 code/CdGF_AUCRF.Rmd
intialize calibration plot code

---
title: "CdGF_aucrf"
author: "Nicholas Lesniak"
date: "September 15, 2016"
output: html_document
---

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
euth_otu_feat <- rf_early_aucrf$Xopt

>>>>

---
title: "CdGF_aucrf"
author: "Nicholas Lesniak"
date: "January 10, 2016"
output: html_document
---

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')

xyplot(calibration(Predict_early_euth_df$Euth_Early~otu_euth_probs[,1]))

cal_plots <- function(observed_col, prediction_df){
  histo_plot <- ggplot(data.frame(prediction_df), aes(x=X1)) + 
    stat_bin(bins = 20, aes(y = ..count../sum(..count..))) +
    scale_x_continuous(breaks=c(seq(0,1,0.2))) +
    labs(x = 'Predicted Value', y = 'Fraction of Samples') + 
    theme_bw()
  cal_plot <- data.frame(observed = observed_col, 
                         predicted = prediction_df[,2],
                         bin = cut(prediction_df[,2], 
                                   breaks =c(-Inf,seq(0.1,0.9,0.1), Inf),
                                   labels = seq(0.05,0.95,0.1))) %>% 
    group_by(bin) %>% 
    summarise(positive_portion = sum(observed==1)/length(observed)) %>% 
    mutate(bin = as.numeric(as.character(bin))) %>% 
    ggplot(aes(x=bin, y=positive_portion)) + geom_point() +
      labs(x='Predicted Value', y='Fraction of Positives') +
      geom_abline(color='gray', intercept = 0, slope = 1) + 
      scale_x_continuous(breaks=c(seq(0,1,0.2)), limits=c(0,1)) +
      scale_y_continuous(breaks=c(seq(0,1,0.2))) +
      theme_bw()
  return(list(histo_plot, cal_plot))
}
test <- cal_plots(observed_col = Predict_early_euth_df$Euth_Early,
          prediction_df = otu_euth_probs)
test[[2]]

otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
euth_otu_feat <- rf_early_aucrf$Xopt
